---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Getting Started {#DataManip3}

```{r tidyr3, echo = FALSE, message = FALSE, warning = FALSE}

library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=50), tidy = FALSE)

```

## Setup

The setup files will get you ready for your analysis. It loads you libraries, needed tables, created directories for your outputs, and assigns some parameter values. 


```{r setup}

min.yr <-2018
max.yr <- 2023 #needs changes with each analysis

ID<- "YOURUSERNAME" #change this to your NatureCounts user ID. You will need to request permission to access the QC NOS data from the NatureCounts.  
req_id = 21345 #Enter your QCNOS request it to your received from NatureCounts to download the data.

source("00-setup.R") #loads packages on other need files for the analysis

#load the map layer
qq <- rnaturalearth::ne_states(country = "canada", returnclass = "sf") %>% st_transform(epsg6703km) 
qq<-qq %>% filter(name=="Québec")

```

## Choose a collection to be downloaded and prepare the provincial basemap

```{r downloaddata, echo = TRUE, message = FALSE}

#list the collections
list.coll<-unique(anal.param$collection)
list.prot<-unique(anal.param$protocol_id)

#select your collection manually for data cleaning
collection <- "QCOWLS"

```

## Output Tables

Create the output tables. This only needs to be done once per analysis

```{r data manip}

source("i-output.R") #Total count period output tables
```


## Data manipulations 

```{r data manip}

source("ii-datamanip.R") #You will be prompted for you NatureCounts password. 

#Because the code looks to see if you have a copy of the data saved first, you may get an error message. This is normal.
#As long as you have output (Events, Map, DataClean) in your `Output` folder, you can ignore this message.

```

## Data Analysis

```{r analysis}

source("iii-QCAnalysis.R")

```

